---
title: "Ethos 'Essence of Research Leadership' Feedback"
subtitle: "November 2023"
#author: "Jen Beaudry"
#date: "25/11/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Jen Beaudry} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)
options(knitr.kable.NA = '')
```


```{r library, include=FALSE}
library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)
library(captioner)

# devtools::install_github("adletaw/captioner")

```

```{r functions, include=FALSE}

source(here("..", "functions", "read_qualtrics.R"))
source(here("..", "functions", "meta_rename.R"))
source(here("..", "functions", "ratings_summary.R"))

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```

```{r load data, include=FALSE}

df <- here::here("data", "ethos_feedback_2023.csv") %>%
  read_qualtrics(legacy = FALSE) %>%
  filter(!is.na(expectations)) %>%  # delete those who didn't answer any questions 
  select(-c("start_date":"user_language", "sc0")) %>% 
  mutate(id = 1:n()) %>% 
  relocate (id)

# number invited to participate in the workshop
participants <- 15

```


```{r recode with metadata, include=FALSE}

# load metadata 

meta <- read_csv(here::here("data", "ethos_metadata_2023.csv"), lazy = FALSE) %>%
  filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables

# recode variable labels according to metadata

df <- meta_rename(df = df, metadata = meta, old = old_variable, new = new_variable)

```


```{r code factors, include=FALSE}


# turn all ratings variables into factors, use datapasta to do this!
# the code below works

df$expectations_met <-  factor(df$expectations_met,levels = c("Did not meet my expectations",
    "Partly met my expectations",
    "Met my expectations",
    "Exceeded my expectations"))

df$post_phd <- factor(df$post_phd, levels = c("Less than 5 years post-PhD", 
                                                  "5 to 10 years post-PhD", 
                                                  "11 to 15 years post-PhD", 
                                                  "More than 15 years post-PhD"))

# work with all rating items together because they have the same levels

cols <- c("workshop_understanding",
  "trainer_expert",
  "trainer_engaging",
  "balance",
  "work_pref_analysis",
  "content_relevance",
  "content_useful",
  "attend")

# turn the cols columns into factors
df <- df %>% 
  dplyr::mutate(across (all_of(cols), ~factor(., 
                                       levels = c("NA",
                                           "Strongly disagree",
                                           "Somewhat disagree",
                                           "Neither agree nor disagree",
                                           "Somewhat agree",
                                           "Strongly agree"))))

```


```{r captions, include = FALSE}

table_nums(name = "career_stage", 
           caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'")

table_nums(name = "expectations", 
           caption = "'What did you expect from this workshop?'")

table_nums(name = "expectations_comment", 
           caption = "'Please elaborate on how the workshop aligned with your expectations.'")

table_nums(name = "action", 
          caption = "'Did this workshop inspire you to take any immediate action(s)?'")

table_nums(name = "best_parts",
             caption = "'What were the best parts of the workshop?'")

table_nums(name = "improvement",
             caption = "'Any suggestions for improvement?'")

table_nums(name = "anything_else",
             caption = "'Anything else you want us to know?'")

fig_nums(name = "ratings_summary", 
         caption = "Ratings of different aspects of the workshop")


```

Mark Douglas from Ethos designed and delivered the *Essence of Research Leadership* 
workshop. The workshop included 2 full-day sessions in November 2023 and will include
a half-day follow-up session in February 2024. This anonymous survey was conducted 
after the second full-day session. Of the `r participants` participants who attended 
the workshop, `r nrow(df)` completed the feedback survey.

We asked participants to rate a number of items about the workshop and the trainer 
on a scale from 'strongly disagree' to 'strongly agree' (see 
`r fig_nums(name = "ratings_summary", display = "cite")`).

\
`r fig_nums(name = "ratings_summary")`

```{r creating tibbles for all ratings, include = FALSE}

# get total n to calculate percentages

total_n <- length(df$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

ratings <- df %>% 
  select (c("workshop_understanding",
  "trainer_expert",
  "trainer_engaging",
  "balance",
  "work_pref_analysis",
  "content_relevance",
  "content_useful",
  "attend"))

# UPDATE THE COLUMNS PARAMETER WITH THE STRINGS FROM ABOVE

columns <- c("workshop_understanding",
  "trainer_expert",
  "trainer_engaging",
  "balance",
  "work_pref_analysis",
  "content_relevance",
  "content_useful",
  "attend")

# RUN THE FUNCTION & APPLY TO ALL COLUMNS IN OUR DF

ratings_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(ratings, column)
})

# remove the NA responses
ratings_summary <- na.omit(ratings_summary)


# also, figure out how many responded with the agree ratings. I use these in the 
  # text summaries later

```


```{r plot the ratings}

# Relevel the responses [changes order in ggplot, but not the dataframe]
# plot it first to see if I need to do this

# tor_rating$rating <- factor (rating$rating, levels = c("Strongly agree",
#                                            "Somewhat agree",
#                                            "Neither agree nor disagree",
#                                            "Somewhat disagree",
#                                            "Strongly disagree"))

# put them in reverse order of how I want them to appear
ratings_summary$rating_item <-
  factor (
    ratings_summary$rating_item,
    levels = c(
      "attend",
      "content_useful",
      "content_relevance",
      "work_pref_analysis",
      "balance",
      "trainer_engaging",
      "trainer_expert",
      "workshop_understanding"
    )
  )

# this is useful to create the plot_labs, but it doesn't need to run each time

# labs <- meta %>%
#   filter(scale == "ratings") %>%
#   pull(item_text_short) %>%
# datapasta::vector_paste_vertical()


# plot it

ggplot(ratings_summary, aes(fill = rating, y = percentage, x = rating_item)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  scale_fill_brewer(
    palette = "Blues",
    na.value = "grey50",
    direction = 1,
    labels = c(
      "N/A",
      "Strongly disagree",
      "Somewhat disagree",
      "Neither agree nor disagree",
      "Somewhat agree",
      "Strongly agree"
    )
  ) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_x_discrete(
    labels = c("I would attend another workshop \nfrom this trainer.", 
               "The content will be useful in my \nfuture role(s).",
               "The content was relevant to my \ncurrent role.",
                "The Work Preference Analysis \nprovided valuable insights.",
                "There was a good balance of \ngroup discussion and presentation.",
               "The trainer was engaging.",
               "The trainer is an expert in the \nsector.",
               "I gained a greater understanding of \nresearch leadership"
 )
) +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

# FYI: the labels are always in opposite directions from the data set!

```

\newpage

```{r expectations data, include = FALSE}

expect <- df %>% 
    dplyr::group_by (expectations_met) %>% 
  count()

```


```{r careerstage, include = FALSE}

# remove the post-PhD because it's repeated in every response
df$post_phd <- str_remove(df$post_phd, " post-PhD")


years <- df %>% 
    dplyr::group_by (post_phd) %>% 
  count()

# change the text to be used in the markdown
years$post_phd <- str_replace(years$post_phd, "Less", "less")

```

We had a mix of participants in this workshop (nominated by their Deans of Research). 
The respondents to the survey reflected this mix; `r years[1,2]` respondents
were `r years [1,1]` post-PhD, `r years[2,2]` respondents were `r years [2,1]` post-PhD,
and `r years[3,2]` respondent was `r years [3,1]` post-PhD. 

We asked respondents how the program aligned with their expectations. 
Of the `r nrow(df)` respondents, 
`r round((expect[4,2]/nrow(df))*100,2)`% indicated that it exceeded their expectations, 
`r round((expect[3,2]/nrow(df))*100,2)`% indicated that it met their expectations, 
`r round((expect[2,2]/nrow(df))*100,2)`% indicated that it partly met their expectations, and 
`r round((expect[1,2]/nrow(df))*100,2)`% indicated that it exceeded their expectations. 

Participants also reported 
whether or not the program aligned with their career stage and elaborated on their 
response (see `r table_nums("career_stage", display = "cite")`).

\
`r table_nums(name = "career_stage")`

```{r career_stage table, include = TRUE}

career_stage <- df %>% 
  select(c(id, post_phd, career_stage_yes, career_stage_no)) %>% 
  replace_na(list(careerstage_yes = "", careerstage_no = "")) %>% 
  arrange(desc(post_phd))


kable(
  career_stage,
  longtable = T,
  booktabs = T, 
  align = c('clll'),
  linesep = "\\addlinespace",
 # caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'",
  col.names = c("Participant", "Years post PhD", "Reasons why it was appropriate", "Reasons why it was not appropriate")
  ) %>%
  column_spec (column = 3, width = "5cm") %>%
   column_spec (column = 4, width = "5cm") %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))

```

\
`r table_nums("expectations", display = "cite")` reports what the respondents
said they expected from the workshop. Their explanations of how the program aligned with their expectations are shown 
in `r table_nums("expectations_comment", display = "cite")`. 

\
`r table_nums(name = "expectations")`

```{r expectations table, include = TRUE}

expectations <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expectations) %>% 
  filter (!is.na(expectations))


kable(
  expectations,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
 # caption = "'What did you expect from this workshop?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\
`r table_nums(name = "expectations_comment")`

```{r expectations elaboration table, include = TRUE}

expectations_comment <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expectations_comment) %>% 
  filter (!is.na(expectations_comment))


kable(
  expectations_comment,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
#  caption = "'Please elaborate on how the workshop aligned with your expectations.'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\newpage
We also asked the participants if the workshop inspired them to take any immediate
actions (see `r table_nums("action", display = "cite")`).

\
`r table_nums(name = "action")`

```{r action table, include = TRUE}

action <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, actions) %>% 
  filter (!is.na(actions))


kable(
  action,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
#  caption = "'Did this workshop inspire you to take any immediate action(s)?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```

\newpage
We asked the participants what they thought were the best parts of the workshop
(see `r table_nums("best_parts", display = "cite")`).

\
`r table_nums(name = "best_parts")`

```{r best_parts table, include = TRUE}

best <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, best_parts) %>% 
  filter (!is.na(best_parts))

kable(
  best,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
#  caption = "'What were the best parts of the workshop?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```
\newpage
We asked the participants if they had any suggestions to improve the workshop
(see `r table_nums("improvement", display = "cite")`).

\
`r table_nums(name = "improvement")`

```{r improvement table, include = TRUE}

improve <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, improvement) %>% 
  filter (!is.na(improvement))


kable(
  improve,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
#  caption = "'Any suggestions for improvement?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))

```
\newpage
Finally, we asked the participants if there was anything else they wanted us to know
(see `r table_nums("anything_else", display = "cite")`).

\
`r table_nums(name = "anything_else")`


```{r anything else table, include = TRUE}

anything_else <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, anything_else) %>% 
  filter (!is.na(anything_else))


kable(
  anything_else,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
#  caption = "'Anything else you want us to know?'",
  col.names = c("Participant", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  kable_styling(latex_options = c("HOLD_position"))


```


If you have any questions, please contact Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in Research Development and Support. 
